---
title: "StatisticsForRoboticSystemsA2"
author: "Sergio"
date: "12/11/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r libs}
library(readxl)
#library(magrittr)
#library(tidyverse)
#library(rstatix)
#library(ggpubr )
library(PMCMRplus)
```

## Import data

Firs we import our data. Three outcomes variables were measured: time, distance, and kinematic estimation error (kte). Four conditions were tested: Adaptive Waypoint with Non-linear control (AN), Adaptive Waypoint with Proportional control (AP), Fixed Waypoint with Non-linear control (FN), Fixed Waypoint with Proportional control (FP).

```{r importdata}
data <- read_excel("data.xlsx")
data$id <- as.factor(data$id)
data$condition <- as.factor(data$condition)
summary(data)
```

## Normality tests
We carry normality tests. Shapiro Wilk's test was used due to the small sample size. The null hypothesis for this test is that the sample distribution is normal.

```{r norm}
norm_time <- shapiro.test(data$time)
distance <- shapiro.test(data$distance)
kte <- shapiro.test(data$kte)

print(norm_time)
print(distance)
print(kte)
```

## Friedman tests
Last tests rejected null hypothesis, hence Friedman is applied instead of ANOVA. This tests was chosen to assess differences between multiple conditions, with matched samples (i.e., same robot), and continuous/interval outcome variable. The null hyphotesis is that all conditions are equal.

```{r friedman}
friedman_time <- friedman.test(data$time, data$condition, data$id )
friedman_distance <- friedman.test(data$distance, data$condition, data$id )
friedman_kte <- friedman.test(data$kte, data$condition, data$id )

print(friedman_time)
print(friedman_distance)
print(friedman_kte)
```

## Posthoc tests
Last tests rejected null hypothesis. Posthoc test are required for pairwise comparisons between conditions. The Bonferroni correction was chosen, as it is the standard for this test in literature.

```{r post}
posthoc_time = frdAllPairsConoverTest(y=data$time, groups=data$condition, blocks=data$id, p.adjust="bonferroni")
posthoc_distance = frdAllPairsConoverTest(y=data$distance, groups=data$condition, blocks=data$id, p.adjust="bonferroni")
posthoc_kte = frdAllPairsConoverTest(y=data$kte, groups=data$condition, blocks=data$id, p.adjust="bonferroni")

print(posthoc_time)
print(posthoc_distance)
print(posthoc_kte)
```
